Lavaging Geographic Information in Deep Neural Networks for Image Understanding

### 2018-06-25 chapters/introduction/introduction.tex
snapshot

Among algorithms that are developed to address these sub-tasks, deep
neural networks (DNNs) rise as stars in recent years. Methods that
uses DNNs achieve state-of-the-art performances in many computer
vision areas (\todo{citations}). As parametric algorithms, deep neural
networks require training for their parameters. Methods to train DNNs
include supervised algorithms, unsupervised algorithms, and
reinforcement learning. Supervised algorithms are the most popular and
commonly applied in many computer vision areas, thanks to their good
performances and the fact that they are easy to implement. However,
supervised learning approaches are sensitive to the quality of data
annotations. In some applications like overhead image segmentation and
transient attributes estimation, data with noise-free annotation is
either limited in quantity or technically difficult to acquire.
In this thesis, we use domain adaptation and weak supervision to
counter this drawback. Our methods focus on lavaging the camera
geometric information to deal with the challenges caused by the lack
of noise-free annotations during DNN training.
The insight behind it is that the camera geometry affects the way that
images manifest objects/scenes, it is possible to exploit the relation
between the camera geometry and image semantics to understand images
better.

@@

In the camera pin-hole model, camera geometry denotes the camera
both intrinsic and extrinsic parameters. The intrinsic parameters
encode the information of the camera itself such as focal length,
principal point \etc; the extrinsic parameters are referred to as the
external states of the camera, such as the camera poses and
offset/location under some coordinate system. In this work, our study
of the camera geometry mainly includes the extrinsic like camera pose
and the geo-orientation/geo-localization of the camera.

>>>>

Among algorithms that are developed to address these sub-tasks, deep
neural networks (DNNs) rise as stars in recent years. Methods that
uses DNNs achieve state-of-the-art performances in many computer
vision areas (\todo{citations}). As parametric algorithms, deep neural
networks require training for their parameters. Methods to train DNNs
include supervised algorithms, unsupervised algorithms, and
reinforcement learning. Supervised algorithms are the most popular and
commonly applied in many computer vision areas, thanks to their good
performances and the fact that they are easy to implement. However,
supervised learning approaches are sensitive to the quality of data
annotations. In some applications like overhead image segmentation and
transient attributes estimation, data with noise-free annotation is
either limited in quantity or technically difficult to acquire.
In this thesis, Our methods focus on lavaging the camera geographic
information to deal with the challenges caused by the lack of
noise-free annotations during DNN training. The insight is
that the camera geographic information encodes the semantic
information because it is related to the appearances of
the scenes.

The process of estimating the camera geographic information is
referred to as geo-calibration. The goal is to estimate the geographic
location and the geo-orientation of the given camera. 
Compared to the common camera calibration, geo-calibration focuses on
calibrating the camera in the geographic coordinates.

Geographic
information reveals the scene appearances

@@

### 2018-06-25 chapters/introduction/junk.tex
snapshot

>>>>

In the camera pin-hole model, camera geometric parameters consists of
the camera intrinsics and the extrinsics. The intrinsic parameters of
a camera encode information of the camera itself such as focal length,
principal point \etc; the extrinsic parameters are referred to as the
external states of the camera, such as the camera poses and
offset/location under some coordinate system. In this work, our study
of the camera geometry mainly includes the extrinsic like camera pose
and the geo-orientation/geo-localization of the camera.
